\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-03-05 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
Buildbot ran the code beautifier.

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team:
in alphabetical order,
Jean-Paul (Pablo) Ampuero,
Kangchen Bai,
Piero Basini,
C\'eline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Percy Galvez,
Dominik G\"oddeke,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Jean-Pierre Vilotte,
Zhinan Xie,
Hejun Zhu.\\

>>>>

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team:
in alphabetical order,
Jean-Paul (Pablo) Ampuero,
Kangchen Bai,
Piero Basini,
C\'eline Blitz,
Alexis Bottero,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Paul Cristini,
Percy Galvez,
Dominik G\"oddeke,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Jean-Pierre Vilotte,
Zhinan Xie,
Chang-Hua Zhang,
Hejun Zhu.\\
